Replication for figures and graphs

### 2024-02-11 outputs/replication/replication.qmd
change the names of datasets

```{r}
#| message: false
#| echo: false
# Read the dataset
main_clean <- read_dta(here("inputs/data/01_main_exp_clean.dta"))
follow_up_clean <- read_dta(here("inputs/data/02_follow_up_clean.dta"))
online_survey_clean <- read_dta(here("inputs/data/03_1st_online_svy_clean.dta"))
```

>>>>

```{r}
#| message: false
#| echo: false
# Read the dataset
main_clean <- read_dta(here("inputs/data/01_main_exp_clean_original.dta"))
follow_up_clean <- read_dta(here("inputs/data/02_follow_up_clean_original.dta"))
online_survey_clean <- read_dta(here("inputs/data/03_1st_online_svy_clean_original.dta"))
```
